Towards Practical First-Order Model Counting

### 2024-04-17 doc/paper.tex
Modify the overview diagram (and lots of other changes)

\SetKwFunction{Crane}{Compile}
\SetKwFunction{Propagate}{Propagate}
\SetKwFunction{FindBaseCases}{FindBaseCases}

@@

\begin{figure*}[t]
  \centering
  \begin{tikzpicture}
    \node at (0, 0) (formula) {$\phi$};
    \node[draw,rounded rectangle] at (3, 0) (alg1) {\Cref{alg:main}};
    \node[draw,rounded rectangle] at (6, 0) (simplification) {Simplification};
    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compilation};

@@

    \node[draw,rounded rectangle] at (3, -2) (alg2) {\Cref{alg1}};
    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\textsc{Crane}};
    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Cref{alg2}};

    \node[draw,fit={(alg1) (simplification) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
    \node at (1.1, 0.5) {\Cranetwo};

    \draw[-Latex] (formula) -- (alg1);
    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (simplification);
    \draw[-Latex] (simplification) -- node[above] {$\mathcal{E}'$} (compilation);
    \draw[-Latex] (compilation) -- (cpp);
    \draw[-Latex] (sizes) -- (cpp);
    \draw[-Latex] (cpp) -- (count);

    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
    \draw[-Latex,dashed] (alg1) -- node[midway] {uses} (alg2);
    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (alg3);
  \end{tikzpicture}
  \caption{Using \Cranetwo{} to compute the model count of formula $\phi$.\ The
    formula is compiled into a set of equations $\mathcal{E}$, which are then
    algebraically simplified and compiled to a C++ program. This program can
    then be run with different command line arguments to compute the model count
    of $\phi$ for various domain sizes.}
\end{figure*}

@@

@@

@@

\paragraph{The \FO{} Logic (After Skolemization)}
\begin{itemize}
  \item Although existential quantifiers are supported, here we describe the
        format used internally. During preprocessing, all existential
        quantifiers are eliminated using
        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
        rewritten into a conjunction of clauses, each of which is in
        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
  \item In the spirit of keeping sorts implicit, we always assume formulas `type
        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
        $x \ne c$ are all part of the formula (for some predicate $P$, variables
        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
        sort.
  \item A \emph{formula} is a conjunction of clauses.
  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
        }\forall x_{2} \in \Delta_{2}\dots\text{
        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
        where $\phi$ is a disjunction of literals that only contain variables
        $x_{1}, \dots, x_{n}$ (and any constants).
  \item A \emph{literal} is either an atom or its negation.
  \item An \emph{atom} is either:
  \begin{itemize}
    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
          $t_{1}, \dots, t_{m}$ or
    \item $x=y$ for some terms $x$ and $y$
  \end{itemize}
  \item An atom is \emph{ground} if it contains no variables (i.e., only
        constants).
  \item The \emph{arity} of a predicate is the number of arguments it takes,
        i.e., $m$ in the case of predicate $P$.
  \item When we want to denote a predicate together with its arity, we write
        $P/m$.
  \item A \emph{term} is either a variable or a constant.
  \item Throughout the paper, we use set-theoretic notation, interpreting a
        formula as a set of clauses and a clause as a set of literals. Moreover,
        for readability, clauses written on separate lines are implicitly
        conjoined.
\end{itemize}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item explain how this works for function calls too
    \item introduce the Iverson bracket (somewhere)
    \item reorder the Logic subsection to cover \FO{} before comparing it to
          other logics (and clarify the differences between the input format and
          the internal format)
    \item (somewhere) mention the trick about increasing the number of sorts
  \end{itemize}
}

\begin{definition}
  A \emph{function call} is $f(x_{1} - c_{1}, \dots, x_{n} - c_{n})$ (written
  $f(\mathbf{x} - \mathbf{c})$ for short), where $f$ is an $n$-ary function,
  each $x_{i}$ is a variable, and each $c_{i}$ is a non-negative constant.
\end{definition}
\todo[inline]{do I ever use this notation for the case when some of the
  variables don't exist?}

\begin{definition}
  A \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written $f(\mathbf{x})$ for
  short), where $f$ is an $n$-ary function, and each $x_{i}$ is a variable. The
  signature of a function call $f(\mathbf{x} - \mathbf{c})$ is $f(\mathbf{x})$.
  For example, the signature of $f(x - 1, y - 2)$ is $f(x, y)$.
\end{definition}

\paragraph{Additional notation}
We write $\expr{}$ for an arbitrary algebraic expression. In the context of both
algebra and logic, we write $C[x \mapsto y]$ for $C$ with all occurrences of $x$
replaced with $y$.

\begin{definition}
  An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
  signature, and $\expr{}$ is an algebraic expression. Henceforth, we call
  $f(\mathbf{x})$ and $\expr{}$ the left-hand side (LHS) and the right-hand side
  (RHS) of the equation, respectively.
\end{definition}

\begin{definition}
  A \emph{base case} is a function call where all arguments are either variables
  or constants (i.e., there is no subtraction within any argument), and there is
  at least one constant. We denote a base case in the same way as a signature,
  e.g., $f(\mathbf{x})$.
\end{definition}

\todo[inline,caption={}]{
  an example of a formula that:
  \begin{itemize}
    \item introduces a new variable,
    \item calls itself.
  \end{itemize}
}

@@

\begin{algorithm}[t]
  \caption{The main part of \Cranetwo{} that compiles a formula into a set of
    equations, including the base cases of recursive functions}\label{alg:main}
  \KwIn{formula $\phi$}
  \KwOut{set $\mathcal{E}$ of equations}
  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
    $\psi \gets \mathcal{F}(f)$\;
    \ForEach{$i$ such that $x_{i}$ is a constant}{
      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
    }
    $(\mathcal{E}', \text{\textunderscore}, \text{\textunderscore}) \gets \Crane{$\psi$}$\;
    $\mathcal{E} \gets \mathcal{E} \cup \mathcal{E}'$\;
  }
\end{algorithm}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item extend it to work with base cases that are themselves recursive
    \item \textsc{Crane}, \Cranetwo{}, or \Crane (here and elsewhere)?
  \end{itemize}
}

@@

  $\mathcal{B} \gets \emptyset$\;
  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
      \ForEach{$c_{i} \in \mathbf{c}$}{
        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto n] \,\}$\;\label{line:insert}
        }
      }
    }
  }
\end{algorithm}

@@

\begin{algorithm}[t]
  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
  \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
  \KwOut{formula $\phi'$}
  $\phi' \gets \emptyset$\;
  \uIf{$n = 0$}{
    \ForEach{clause $C \in \phi$}{
      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
      $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
      \If{$\Delta \in \Doms(C)$ {\bf and} $C' \ne \emptyset$}{
        $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
        $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;\label{line:smoothing2}
      }
    }
  }
  \Else{
    $c \gets$ a new constant in $\Delta$\;
    \ForEach{clause $C \in \phi$}{
      $C' \gets C$\;
      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
        $C' \gets C'[v \mapsto c]$\;
      }
      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
    }
  }
\end{algorithm}

We use \cref{alg2} to find the transformed formula corresponding to each base
case obtained using \cref{alg1} and call \textsc{Crane} on the formula to obtain
the required base cases.
% TODO: or crane 2?

\begin{itemize}
  \item Clauses where all literals have variables quantified over the empty
        domain are still removed.
  \item $C'$ is guaranteed to be non-empty.
  \item \Cref{line:smoothing1,line:smoothing2} are explained in
        \cref{sec:smoothingbase}.
\end{itemize}

@@

\begin{description}
  \item[\texttt{Ref}.] During smoothing, when unit clauses (a.k.a.\ variables)
        are propagated in the opposite direction of the FCG arcs (i.e.,
        `upwards'), when visiting a \texttt{Ref} node, these clauses are
        translated using the domain map of the \texttt{Ref} node. For example,
        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
        mentions $\Delta$, then replace it by $\Delta'$.
  \item[Constraint removal.] Do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $x \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall x \in \Delta'\text{. }\phi(x)$ with
        $\forall x \in \Delta\text{. }X \ne c \Rightarrow \phi(x)$.
  \item[Domain recursion.] Suppose the domain recursion node introduces constant
        $c \in \Delta$. For each unit clause received from the child node,
        replace each occurrence of $\phi(x)$ or $\forall x \in \Delta\text{.
        } x \ne c \Rightarrow \phi(x)$ with $\forall x \in \Delta\text{.
        }\phi(x)$. This can be seen as a claim about what ground atoms the
        domain recursion node \emph{should} cover (or a temporary assumption).
        If the relevant subgraph indeed covers those ground atoms, Stage~2 will
        do nothing. Otherwise, smoothing nodes will be added below the domain
        recursion node to cover the difference between what was propagated from
        the domain recursion node and what was received from the child node.
\end{description}
\todo[inline]{Add examples of both cases, with figures.}

@@

The target is to generate C++ code that can evaluate numerical values of the
model counts based on the equations generated by \textsc{Crane}. We achieve this
by parsing the equations generated by \textsc{Crane}, simplifying them, and then
generating C++ code. This approach can be done in linear time in the length of
the formula using
the
\href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
  Yard Algorithm}.

The translation of a set $\mathcal{E}$ of equations into a C++ program works as
follows.

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Maybe add some complete examples of C++ programs in the supplementary
          material.
          \item Later on:
          \begin{itemize}
            \item Eliminate (e.g., Emacs) warnings.
            \item must run it by A\&G
            \item re-check submission instructions and formatting guidelines
            \item Full stop at the end of a single-sentence caption?
          \end{itemize}
  \end{itemize}
}

>>>>

\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
\SetKwFunction{Crane}{Compile}
\SetKwFunction{Propagate}{Propagate}
\SetKwFunction{FindBaseCases}{FindBaseCases}
\SetKwFunction{Simplify}{Simplify}

@@

\begin{figure*}[t]
  \centering
  \begin{tikzpicture}
    \node at (-1, 0) (formula) {$\phi$};
    \node[draw,rounded rectangle] at (3, 0) (alg1) {\CompileWithBaseCases};
    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};

@@

    \node[draw,rounded rectangle] at (3, -2) (alg2) {\FindBaseCases};
    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\Crane};
    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Propagate};
    \node[draw,rounded rectangle,right = 0.1cm of alg3] (simplify) {\Simplify};

    \node[draw,fit={(alg1) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
    \node at (0.2, 0.5) {\Cranetwo};

    \draw[-Latex] (formula) -- (alg1);
    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (compilation);
    \draw[-Latex] (compilation) -- (cpp);
    \draw[-Latex] (sizes) -- (cpp);
    \draw[-Latex] (cpp) -- (count);

    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg2);
    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg3);
    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (simplify);
  \end{tikzpicture}
  \caption[]{The outline of using \Cranetwo{} to compute the model count of a
    formula $\phi$. The formula is compiled into a set of equations
    $\mathcal{E}$ that are then compiled to a C++ program. This program can then
    be run with different command line arguments to compute the model count of
    $\phi$ for various domain sizes. \CompileWithBaseCases makes use
    of: \begin{enumerate*}[label=(\roman*)]
      \item the knowledge compilation algorithm of \textsc{Crane} (denoted by \Crane),
      \item a procedure for identifying a sufficient set of base cases (denoted by \FindBaseCases),
      \item a procedure for constructing a formula that corresponds to a given base case (denoted by \Propagate), and
      \item algebraic simplification techniques (denoted by \Simplify).
    \end{enumerate*}
  }\label{fig:overview}
\end{figure*}

\todo[inline]{By pointing to the outline in \cref{fig:overview}, make forward
  references to the sections of the paper.}

@@

We write $\mathbb{N}_{0}$ for the set of non-negative integers. In the context
of both algebra and logic, we write $C[x \mapsto y]$ for $C$ with all
occurrences of $x$ replaced with $y$.

@@

\todo[inline]{Reorder the Logic subsection to cover \FO{} before comparing it to
  other logics (and clarify the differences between the input format and the
  internal format)}

@@

\paragraph{The \FO{} Logic (After Skolemization)}
\begin{itemize}
  \item Although existential quantifiers are supported, here we describe the
        format used internally. During preprocessing, all existential
        quantifiers are eliminated using
        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
        rewritten into a conjunction of clauses, each of which is in
        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
  \item In the spirit of keeping sorts implicit, we always assume formulas `type
        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
        $x \ne c$ are all part of the formula (for some predicate $P$, variables
        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
        sort.
  \item A \emph{formula} is a conjunction of clauses.
  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
        }\forall x_{2} \in \Delta_{2}\dots\text{
        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
        where $\phi$ is a disjunction of literals that only contain variables
        $x_{1}, \dots, x_{n}$ (and any constants).
  \item We say that a clause is a \emph{(positive) unit clause} if:
        \begin{itemize}
          \item there is only one literal with a predicate, and
          \item it is a positive literal.
        \end{itemize}
  \item A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or
        its negation (i.e., a \emph{negative} literal).
  \item An \emph{atom} is either:
  \begin{itemize}
    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
          $t_{1}, \dots, t_{m}$ or
    \item $x=y$ for some terms $x$ and $y$
  \end{itemize}
  \item An atom is \emph{ground} if it contains no variables (i.e., only
        constants).
  \item The \emph{arity} of a predicate is the number of arguments it takes,
        i.e., $m$ in the case of predicate $P$.
  \item When we want to denote a predicate together with its arity, we write
        $P/m$.
  \item A \emph{term} is either a variable or a constant.
  \item Throughout the paper, we use set-theoretic notation, interpreting a
        formula as a set of clauses and a clause as a set of literals. Moreover,
        for readability, clauses written on separate lines are implicitly
        conjoined.
\end{itemize}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item the definition of a function is a strong assumption
    \item the notation for a function call is now outdated
  \end{itemize}
}

\begin{itemize}
  \item We write $\expr{}$ for an arbitrary algebraic expression.
  \item A few terms have different meanings in the context of algebra as
        compared to logic:
        \begin{itemize}
          \item a \emph{variable} is either:
                \begin{itemize}
                  \item a parameter of a function or
                  \item a variable introduced by a summation, e.g., $i$ in
                        $\sum_{i=1}^{n} \expr$.
                \end{itemize}
          \item A \emph{constant} is a non-negative integer.
        \end{itemize}
\end{itemize}

\begin{definition}
  A (function) \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written
  $f(\mathbf{x})$ for short), where $f$ is an $n$-ary function, and each $x_{i}$
  is a variable.
\end{definition}

\begin{definition}
  Given a function $f$ with signature $f(\mathbf{x})$, a \emph{function call} of
  $f$ is $f(\mathbf{y})$, where each $y_{i}$ is either $x_{i} - c_{i}$ or
  $c_{i}$ for some constant $c_{i} \in \mathbb{N}_{0}$.
\end{definition}

\begin{definition}
  An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
  signature. We refer to $f(\mathbf{x})$ and $\expr{}$ as the \emph{left-hand
    side} (LHS) and the \emph{right-hand side} (RHS) of the equation,
  respectively.
\end{definition}

\begin{definition}\label{def:basecase}
  Let $f$ be a function with signature $f(\mathbf{x})$. Then a \emph{base case}
  of $f$ is a function call $f(\mathbf{y})$ such that either $y_{i} = x_{i}$ or
  $y_{i} \in \mathbb{N}_{0}$ for all $i$, and the latter case applies at least
  once.
\end{definition}

@@

\begin{algorithm}[t]
  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:main}
  \KwIn{formula $\phi$}
  \KwOut{set $\mathcal{E}$ of equations}
  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;
  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
    $\psi \gets \mathcal{F}(f)$\;
    \ForEach{$i$ such that $x_{i} \in \mathbb{N}_{0}$}{
      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
    }
    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;
  }
\end{algorithm}

\todo[inline]{In \cref{alg:main}, some kind of translation also needs to take
  place, right?}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item \textsc{Crane}, \Cranetwo{}, or \Crane in the paragraph below
  \end{itemize}
}

@@

  $\mathcal{B} \gets \emptyset$\;
  \ForEach{equation $(\ldots = \expr{}) \in \mathcal{E}$}{
    \ForEach{function call $f(\mathbf{y}) \in \expr{}$}{\label{line:functioncall}
      let $f(\mathbf{x})$ be the signature of $f$\;
      \ForEach{$y_{i} \in \mathbf{y}$} {
        \uIf{$y_{i} \in \mathbb{N}_{0}$}{
          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$\;
        }
        \ElseIf{$y_{i} = x_{i} - c_{i}$}{
          \For{$j \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
            $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$\;\label{line:insert}
          }
        }
      }
    }
  }
\end{algorithm}

\todo[inline,caption={}]{
  \begin{itemize}
    \item introduce the Iverson bracket (it's only used in this subsection)
    \item \Cref{alg1} is now fixed and supersedes the description below (and the
          code!)
    \item NOTE: exactly one of the if and else-if branches always applies
  \end{itemize}
}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item later check if I'm still using the syntax for $\Vars$, $\Dom$, etc.
    \item align the last line to be a bit neater
    \item \Cref{alg2} now supports any base case domain sizes
    \item NOTE: if $C' = \emptyset$, then the clause becomes irrelevant and
          doesn't need smoothing, so can be skipped
  \end{itemize}
}

\begin{algorithm}[t]
  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
  \KwIn{formula $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
  \KwOut{formula $\phi'$}
  $\phi' \gets \emptyset$\;
  \uIf{$n = 0$}{
    \ForEach{clause $C \in \phi$}{
      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
      \Else{
        $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
        \If{$C' \ne \emptyset$}{
          $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
          $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;\label{line:smoothing2}
        }
      }
    }
  }
  \Else{
    $D \gets \text{a set of $n$ new constants in $\Delta$}$\;
    \ForEach{clause $C \in \phi$}{
      ${(x_{i})}_{i=1}^{m} \gets \text{the variables in $C$ with domain $\Delta$}$\;
      \lIf{$m = 0$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
      \Else{
        $\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$\;
      }
    }
  }
\end{algorithm}

\todo[inline,caption={}]{ Turn these notes into a coherent description (that
  doesn't mention \textsc{Crane}):
  \begin{itemize}
    \item Each base case identified by \FindBaseCases can be interpreted as
          assuming some domain...
    \item \Propagate (\cref{alg2}) to find the transformed formula corresponding
          to each base case identified by \FindBaseCases and call \textsc{Crane}
          on the formula to obtain the required base cases.
    \item Clauses where all literals have variables quantified over the empty
          domain are still removed.
    \item $C'$ is guaranteed to be non-empty.
    \item \Cref{line:smoothing1,line:smoothing2} are explained in
          \cref{sec:smoothingbase}.
  \end{itemize}
}
\todo[inline]{Maybe prove consistency: if two base case overlap, their numerical
  answers also overlap.}

@@

\begin{description}
  \item[\texttt{Ref}.] During smoothing, when unit clauses are propagated in the
        opposite direction of the FCG arcs (i.e., `upwards'), when visiting a
        \texttt{Ref} node, these clauses are translated using the domain map of
        the \texttt{Ref} node. For example, if the domain map include
        $\Delta \mapsto \Delta'$, and the unit clause mentions $\Delta$, then
        replace it by $\Delta'$.
  \item[Constraint removal.] Do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $x \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall x \in \Delta'\text{. }\phi(x)$ with
        $\forall x \in \Delta\text{. }X \ne c \Rightarrow \phi(x)$.
  \item[Domain recursion.] Suppose the domain recursion node introduces constant
        $c \in \Delta$. For each unit clause received from the child node,
        replace each occurrence of $\phi(x)$ or $\forall x \in \Delta\text{.
        } x \ne c \Rightarrow \phi(x)$ with $\forall x \in \Delta\text{.
        }\phi(x)$. This can be seen as a claim about what ground atoms the
        domain recursion node \emph{should} cover (or a temporary assumption).
        If the relevant subgraph indeed covers those ground atoms, Stage~2 will
        do nothing. Otherwise, smoothing nodes will be added below the domain
        recursion node to cover the difference between what was propagated from
        the domain recursion node and what was received from the child node.
\end{description}

@@

The target is to generate C++ code that can evaluate numerical values of the
model counts based on the equations generated by \CompileWithBaseCases. The
translation of a set $\mathcal{E}$ of equations into a C++ program works as
follows.

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Maybe add some complete examples of C++ programs in the supplementary
          material.
          \item Later on:
          \begin{itemize}
            \item Eliminate (e.g., Emacs) warnings.
            \item must run it by A\&G
            \item re-check submission instructions and formatting guidelines
            \item Full stop at the end of a single-sentence caption?
            \item cite the \textsc{Crane} paper (and other algorithms' papers)
                  where necessary
          \end{itemize}
  \end{itemize}
}
